COG-ED Manuscript

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
plot works, also fml

  # H2b
  h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2b_BF <- h2b_full_BF / h2b_null_BF

  # H2c
  h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2c_BF <- h2c_full_BF / h2c_null_BF

@@

  # create interaction plot
  h2c_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa()

@@

  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())

@@

@@

    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
                          predictor = c("Level", "NFC"))
    sca_results <- rbind(sca_results, newdata)

>>>>

  # H2b
  h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
  h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
  h2b_BF <- h2b_full_BF / h2b_null_BF

  # H2c
  h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
  h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
  h2c_BF <- h2c_full_BF / h2c_null_BF

@@

  # create interaction plot
  h2c_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa() +
    scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))

@@

  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character(), BF10 = double())

@@

    # convert random factor to type factor

    sca_data$subject <- factor(sca_data$subject)

    # compute Bayes factor

    sca_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                        data = sca_data, whichRandom = 'subject', progress = FALSE)
    sca_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                        data = sca_data, whichRandom = 'subject', progress = FALSE)
    sca_BF <- sca_full_BF / sca_null_BF

@@

    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
                          predictor = c("Level", "NFC"),
                          BF10 = c(extractBF(sca_BF)$bf, extractBF(sca_BF)$bf))
    sca_results <- rbind(sca_results, newdata)
